External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising

### 2016-10-28 CVPR2017_Review_Unified.tex
ad

\subsection{The Testing Datasets}
The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each scene,  was shot 500 times (with same camera and camera setting). The mean image of the 500 shots is roughly taken as the “ground truth”, with which the PSNR can be computed. Since there are contents in different images, we cropped the 17 images into 60 smaller parts containing different contents. Some samples are shown in Figure \ref{fig4}. The second dataset provided in \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic,ncwebsite}. The third dataset is provided by the Commercial software Neat Image \cite{neatimage}. The second and third dataset do not have ground truth images.

>>>>

\subsection{The Testing Datasets}
The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison. Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts including different contents. Some samples are shown in Figure \ref{fig4}. The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}. The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in PhotoShop . Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed for comparison.
